---
title: "ANEP US Census Bureau and Bureau of Economic Assessment Stats Query"
author: "Ed Sherwood"
date: "January 24, 2019"
output: 
   html_document:
     df_print: paged
     code_folding: hide
     toc: true
     toc_float: true
---

```{r setup, include=FALSE}
library(tidyverse)
library(tidycensus) #Need an api key from US Census Bureau.
library(bea.R) #Need an api key from US BEA.
library(viridis)
library(rgdal)
library(sf)
library(leaflet)
library(rmarkdown)
options(tigris_use_cache = TRUE)
knitr::opts_chunk$set(echo = TRUE)
```

## Get some US Census data

Download US Census data on natural resource dependent jobs (total # and median income) within counties and summarize across NEP boundaries:

```{r Acquire all US Census Data, warning = FALSE, message=FALSE}
nep_sf <- st_read(dsn = "./data-raw", layer = "NEP_Boundaries10162018", quiet = TRUE)
states <- c("AL", "AZ", "AR", "CA", "CO", "CT", "DE", "FL", "GA",
            "ID", "IL", "IN", "IA", "KS", "KY", "LA", "ME", "MD",
            "MA", "MI", "MN", "MS", "MO", "MT", "NE", "NV", "NH", "NJ",
            "NM", "NY", "NC", "ND", "OH", "OK", "OR", "PA", "RI", "SC",
            "SD", "TN", "TX", "UT", "VT", "VA", "WA", "WV", "WI", "WY",
            "PR")

metrics <- load_variables(2017, "acs5", cache = TRUE) %>% 
       filter(grepl("Fishing|fishing", label))

totaljobs_sf <- get_acs(geography = "county", variables = c(Ag_For_Fish_Hunt_Min = "C24050_002"), 
                         state = states, geometry = TRUE)

nr_medinc_sf <- get_acs(geography = "county", variables = c(Med_Income = "B24031_003"), 
                         state = states, geometry = TRUE)

ustotaljobs_sf <- st_transform(totaljobs_sf, st_crs(nep_sf))
usnrmedinc_sf <- st_transform(nr_medinc_sf, st_crs(nep_sf))

nep_jobs_intersects <- st_intersects(nep_sf, ustotaljobs_sf)
nep_medinc_intersects <- st_intersects(nep_sf, nr_medinc_sf)

nep_sel_sf <- ustotaljobs_sf[unlist(nep_jobs_intersects),]
nep_sel2_sf <- nr_medinc_sf[unlist(nep_medinc_intersects),]

nep_jobs <- st_join(nep_sf, nep_sel_sf, join = st_intersects) %>%
                   sf::st_buffer(dist = 0)
nep_nrmedinc <- st_join(nep_sf, nep_sel2_sf, join = st_intersects) %>%
                   sf::st_buffer(dist = 0)

nep_jobs_sum <- nep_jobs %>% 
               select(NEP_NAME, estimate) %>%
               group_by(NEP_NAME) %>% 
               summarise(jobs = sum(estimate))

nep_medinc_sum <- nep_nrmedinc %>% 
               select(NEP_NAME, estimate) %>%
               group_by(NEP_NAME) %>% 
               summarise(medinc = median(estimate))

```

## US Census Natural Resource Dependent Jobs by NEP Project Areas {.tabset}

### Overview Map

Plot US Census natural resource dependent jobs data within the NEP boundaries:
```{r Display Census Job Data as a Map, warning = FALSE, message=FALSE}

pal <- colorNumeric(palette = "viridis", domain = nep_jobs_sum$jobs, n = 10)

nep_jobs_sum %>%
    st_transform(crs = "+init=epsg:4326") %>%
    leaflet(width = "100%") %>%
    addProviderTiles(provider = "CartoDB.Positron") %>%
    addPolygons(popup = ~ paste(NEP_NAME,"</br>","Jobs = ",jobs),
                stroke = FALSE,
                smoothFactor = 0,
                fillOpacity = 0.7,
                color = ~ pal(jobs)) %>%
    addLegend("bottomright", 
              pal = pal, 
              values = ~ jobs,
              title = "Natural Resource Dependent Jobs</br>(Ag.,Forest.,Fishing,Hunting,Mining)",
              opacity = 1)
```

### Data Table

Underlying natural resource dependent jobs estimated within NEP Project Areas:
```{r Display Census NR Jobs by NEP as a Table, warning = FALSE, message=FALSE}
nep_jobs2 <- nep_jobs_sum  %>% 
             select(NEP_NAME, jobs) %>% 
             st_set_geometry(NULL) %>% 
             rename("NEP" = NEP_NAME, "Total Jobs(2015)" = jobs)

nep_jobs2
```

## US Census Natural Resource Dependent Jobs, Median Incomes by NEP Project Areas {.tabset}

### Overview Map

Plot US Census natural resource dependent jobs, median income data within the NEP boundaries:
``` {r Display Census Median Income Data in a Map, warning = FALSE, message=FALSE}
pal2 <- colorNumeric(palette = "viridis", domain = nep_medinc_sum$medinc, n = 10)

nep_medinc_sum %>%
    st_transform(crs = "+init=epsg:4326") %>%
    leaflet(width = "100%") %>%
    addProviderTiles(provider = "CartoDB.Positron") %>%
    addPolygons(popup = ~ paste(NEP_NAME,"</br>","Median Income = ",medinc),
                stroke = FALSE,
                smoothFactor = 0,
                fillOpacity = 0.7,
                color = ~ pal2(medinc)) %>%
    addLegend("bottomright", 
              pal = pal2, 
              values = ~ medinc,
              title = "Natural Resource Dependent Jobs</br>(Median Annual Income)",
              opacity = 1)
```

### Data Table
Underlying natural resource dependent jobs, median incomes estimated within NEP Project Areas:
```{r Display Census Median Income by NEP as a Table, warning = FALSE, message=FALSE}
nep_medinc2 <- nep_medinc_sum  %>% 
             select(NEP_NAME, medinc) %>% 
             st_set_geometry(NULL) %>% 
             rename("NEP" = NEP_NAME, "Median Income ($, 2015)" = medinc)

nep_medinc2
```

## US BEA Natural Resource Dependent Jobs, Total Personal Income by NEP Project Areas {.tabset}


Import US BEA data on natural resource dependent jobs (total county income) and summarize across NEP boundaries:

```{r Acquire all US BEA County Data, warning = FALSE, message=FALSE}

userSpecList <- list('UserID' = '88964E07-8671-4DFB-BF65-4E680DEDA641',
                     'Method' = 'GetData',
                     'datasetname' = 'Regional',
                     'TableName' = 'CAINC5N',
                     'LineCode' = '100',
                     'GeoFIPS' = 'COUNTY',
                     'Year' = '2017')

nr_income <- beaGet(userSpecList, asTable = TRUE) %>% 
                    filter(str_detect(GeoFips, "....0")==FALSE) %>%    
                    mutate(GEOID = as.character(GeoFips))
nr_income$GEOID <- gsub(" ", "", nr_income$GEOID, fixed = TRUE)

nr_inc_sf <- left_join(nep_sel_sf, nr_income, by = c('GEOID' = 'GEOID'))

nep_totinc <- st_join(nep_sf, nr_inc_sf, join = st_intersects) %>%
                   sf::st_buffer(dist = 0)

nep_inc_sum <- nep_totinc %>% 
               select(NEP_NAME, DataValue_2017) %>%
               group_by(NEP_NAME) %>% 
               summarise(totinc = sum(DataValue_2017, na.rm = TRUE))
nep_inc_sum$totinc <- ifelse(nep_inc_sum$totinc==0,NA,nep_inc_sum$totinc*1000)

```

### Overview Map

Plot US BEA natural resource dependent jobs total income estimates within the NEP boundaries (where available):

```{r Plot Natural Resource Dependent Jobs Total Income, warning=FALSE, message=FALSE}
pal3 <- colorNumeric(palette = "viridis", domain = nep_inc_sum$totinc, n = 10)

nep_inc_sum %>%
    st_transform(crs = "+init=epsg:4326") %>%
    leaflet(width = "100%") %>%
    addProviderTiles(provider = "CartoDB.Positron") %>%
    addPolygons(popup = ~ paste(NEP_NAME,"</br>","Total Income (2017) = ",totinc),
                stroke = FALSE,
                smoothFactor = 0,
                fillOpacity = 0.7,
                color = ~ pal3(totinc)) %>%
    addLegend("bottomright", 
              pal = pal3, 
              values = ~ totinc,
              title = "Natural Resource Dependent Jobs</br>(Total Annual Income, if reported)",
              opacity = 1)
```

### Data Table
Underlying natural resource dependent jobs, total personal income estimated within NEP Project Areas:
```{r Display BEA NR Job Total Income by NEP as a Table, warning = FALSE, message=FALSE}
nep_inc2 <- nep_inc_sum  %>% 
             select(NEP_NAME, totinc) %>% 
             st_set_geometry(NULL) %>% 
             rename("NEP" = NEP_NAME, "Total Personal Income ($, 2017)" = totinc)

nep_inc2

```